Modern Graph Generators: A Survey

### 2018-10-19 comparison.tex
Graphalytics and Graph 500 corrections
Minor correction

\begin{tabular}{| c | p{3cm} | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }

@@

\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{Barabasi99emergenceScaling} & -- & -- & Y & N & Y & power-law & edge-list &  N  \\

@@

\multirow{2}{*}{\rot{\textbf{Co}}}

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{5}{*}{\rot{\textbf{General}}}
  & \cite{Barabasi99emergenceScaling} & {\bf x} & & & & x & & \\
\cline{2-9}
   & R-MAT    & {\bf x} & & & & x & & \\
\cline{2-9}
  & GraphGen  & {\bf x} & & x & & & & \\
\cline{2-9}
%  & Graph 500 & {\bf x} & & & & x & & \\
%\cline{2-9}
  & BTER      & {\bf x} & & & & & & \\
\cline{2-9}
  & Darwini   & {\bf x} & & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & LBBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & UOBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & IIMB & & {\bf x} & & & & & \\
\cline{2-9}
 & BSBM & & {\bf x} & & & & & \\
\cline{2-9}
 & SP$^2$Bench & & {\bf x} & & & & & \\
\cline{2-9}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
\cline{2-9}
 & DBPSB & & {\bf x} & & & & & \\
\cline{2-9}
 & LODIB & & {\bf x} & & & & & \\
\cline{2-9}
 & SIB & & {\bf x} & & & & & \\
\cline{2-9}
 & Geographica & & {\bf x} & & & & & \\
\cline{2-9}
 & WatDiv & & {\bf x} & & & & & \\
\cline{2-9}
 & RBench & & {\bf x} & & & & & \\
\cline{2-9}
 & LDBC SPB & & {\bf x} & & & & & \\
\cline{2-9}
 & LinkGen & & {\bf x} & & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & & \\
\cline{2-9}
  & gMark & & x & {\bf x} & x & & & \\
\cline{2-9}
  & graphGen & & & {\bf x} & & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
\cline{2-9}
 & \cite{Yao2011}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LinkBench  & & & x & {\bf x} & & & \\
\cline{2-9}
 & S3G2  & & x & x & {\bf x} & & & \\
\cline{2-9}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LDBC SNB   & & x & x & {\bf x} & & & \\
\cline{2-9}
  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
\hline
\hline   % ======================   graph analytics
\multirow{1}{*}{\rot{\textbf{A}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
%\cline{2-9}
%  & Graphalytics & & & & & {\bf x} & & \\
\hline
\hline   %  ======================  community detection
\multirow{2}{*}{\rot{\textbf{Co}}}
  &  & & & & & & {\bf x} &\\
\cline{2-9}
  &  & & & & & & {\bf x} & \\
%\cline{2-9}
%  & & & & & & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St}}}
  & S2Gen & & & & & & & {\bf x}\\
\cline{2-9}
  & RSPLab & & & & & & & {\bf x} \\
%\cline{2-9}
%  & & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

For example, many general or domain-agnostic graph generators, such as the
preferential attachment~\cite{Barabasi99emergenceScaling} or R-MAT, are typically used to test graph
analytics frameworks when large real graphs are not available. Actually,
Graphalytics uses R-MAT as one as its graph generators for benchmarking graph
analytics.

>>>>

\begin{tabular}{| c | l | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }

@@

\multirow{5}{*}{\rot{\textbf{General}}}
  & Preferential attachment & -- & -- & Y & N & Y & power-law & edge-list &  N  \\

@@

\multirow{3}{*}{\rot{\textbf{Co}}}

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{5}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & & & x & & \\
\cline{2-9}
   & R-MAT    & {\bf x} & & & & x & & \\
\cline{2-9}
  & GraphGen  & {\bf x} & & x & & & & \\
\cline{2-9}
%  & Graph 500 & {\bf x} & & & & x & & \\
%\cline{2-9}
  & BTER      & {\bf x} & & & & & & \\
\cline{2-9}
  & Darwini   & {\bf x} & & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & LBBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & UOBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & IIMB & & {\bf x} & & & & & \\
\cline{2-9}
 & BSBM & & {\bf x} & & & & & \\
\cline{2-9}
 & SP$^2$Bench & & {\bf x} & & & & & \\
\cline{2-9}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
\cline{2-9}
 & DBPSB & & {\bf x} & & & & & \\
\cline{2-9}
 & LODIB & & {\bf x} & & & & & \\
\cline{2-9}
 & SIB & & {\bf x} & & & & & \\
\cline{2-9}
 & Geographica & & {\bf x} & & & & & \\
\cline{2-9}
 & WatDiv & & {\bf x} & & & & & \\
\cline{2-9}
 & RBench & & {\bf x} & & & & & \\
\cline{2-9}
 & LDBC SPB & & {\bf x} & & & & & \\
\cline{2-9}
 & LinkGen & & {\bf x} & & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & & \\
\cline{2-9}
  & gMark & & x & {\bf x} & x & & & \\
\cline{2-9}
  & graphGen & & & {\bf x} & & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
\cline{2-9}
 & \cite{Yao2011}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LinkBench  & & & x & {\bf x} & & & \\
\cline{2-9}
 & S3G2  & & x & x & {\bf x} & & & \\
\cline{2-9}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LDBC SNB   & & x & x & {\bf x} & & & \\
\cline{2-9}
  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
\hline
\hline   % ======================   graph analytics
\multirow{1}{*}{\rot{\textbf{A}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
%\cline{2-9}
%  & Graphalytics & & & & & {\bf x} & & \\
\hline
\hline   %  ======================  community detection
\multirow{3}{*}{\rot{\textbf{Co}}}
  &  & & & & & & {\bf x} &\\
\cline{2-9}
  &  & & & & & & {\bf x} & \\
\cline{2-9}
  &  & & & & & & {\bf x} & \\
%\cline{2-9}
%  & & & & & & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St}}}
  & S2Gen & & & & & & & {\bf x}\\
\cline{2-9}
  & RSPLab & & & & & & & {\bf x} \\
%\cline{2-9}
%  & & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

For example, many general or domain-agnostic graph generators, such as the
preferential attachment~\cite{Barabasi99emergenceScaling} or R-MAT, are typically used to test graph analytics frameworks when large real graphs are not available. %Actually, Graphalytics uses R-MAT as one as its graph generators for benchmarking graph analytics.
